Extended Data

### 2021-10-21 doc/manuscript/Dow_manuscript_Nature.Rmd
earlywood/ latewood references
@cdow, FYI. cool stuff!

First, extra C production in years with warm springs may be allocated to woody growth without affecting diameter growth in the current year. 
It is possible that extra carbon is allocated to cell wall thickening, a process that lags behind stem expansion[@cuny_woody_2015], resulting in formation of more carbon-dense cell walls in years with warm springs (**coauthors, do any of you know studies that have looked at this?**).
Extra carbon could also be saved within trees as non-structural carbohydrates and used towards growth the following year[@trumbore_quantifying_2002;@richardson_seasonal_2013], potentially including an earlier start to growth[@fu_variation_2014]. 
Extension of our tree-ring analysis revealed little correlation between April $T_{max}$ and growth the following year (sig. pos. correlations for 5/142 RP and 3/66 DP species-site combinations, Fig. `r EDF_tree_rings_TMAX_extended`), although predominantly positive (non-significant) correlations in RP species suggests that this dynamic may weakly influence their annual growth.
Thus, warm springs are unlikely to provide substantial, sustained C sinks under warming spring temperatures.

>>>>

First, extra C production in years with warm springs may be allocated to woody growth without affecting diameter growth in the current year. 
It is theoretically possible that extra carbon is allocated to cell wall thickening, a process that lags behind stem expansion[@cuny_woody_2015], or to a thicker layer of higher-density latewood, resulting in formation of more carbon-dense wood in years with warm springs.
However, existing evidence indicates that warm springs have a neutral or negative effect on latewood width[@tardif_influence_2006; @roibu_climatic_2020; @kern_multiple_2013], which is more strongly controlled by summer drought stress[@tardif_influence_2006; @roibu_climatic_2020], suggesting that a positive effect of warm springs total C content of annual rings is unlikely. 
Extra carbon could also be saved within trees as non-structural carbohydrates and used towards growth the following year[@trumbore_quantifying_2002;@richardson_seasonal_2013], potentially including an earlier start to growth[@fu_variation_2014]. 
Extension of our tree-ring analysis revealed little correlation between April $T_{max}$ and growth the following year (sig. pos. correlations for 5/142 RP and 3/66 DP species-site combinations, Fig. `r EDF_tree_rings_TMAX_extended`), although predominantly positive (non-significant) correlations in RP species suggests that this dynamic may weakly influence their annual growth.
Thus, warm springs are unlikely to provide substantial, sustained C sinks under warming spring temperatures.
